---
title: "Database administration"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Database administration}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, eval=FALSE}
library(similR)

raw <- import_article_data("data-raw/input/institutional_articles.csv")

processed <- process_scopus(
  raw,
  column_map = c(
    title = "Title",
    authors = "Authors",
    abstract = "Abstract",
    author_keywords = "Keywords",
    doi = "DOI",
    year = "Year",
    source_title = "Source"
  ),
  source = "generic"
)

processed <- build_dimension_texts(processed)
```

## Lexical-only Release

A lexical Release does not require Python:

```{r, eval=FALSE}
release <- build_database_release(
  data = processed,
  previous_database = NULL,
  data_version = "2026.07",
  output_dir = "release/2026.07"
)

validate_release(release)
```

## Release with semantic embeddings

Prepare the local Python dependencies and download the model once:

```{r, eval=FALSE}
install_semantic_engine()
download_embedding_model()
```

Then generate a complete semantic Release:

```{r, eval=FALSE}
release <- build_database_release(
  data = processed,
  previous_database = "release/2026.06/university_articles_2026-06.duckdb",
  data_version = "2026.07",
  model_name = "intfloat/multilingual-e5-base",
  output_dir = "release/2026.07",
  generate_embeddings = TRUE,
  batch_size = 32L,
  overwrite = TRUE
)

validate_release(release)
```

When the previous database is compatible, unchanged article embeddings are
reused. Only new and modified articles are encoded.

## Files to publish

The output directory contains:

```text
university_articles_2026-07.duckdb
manifest.json
checksums.txt
release_notes.md
```

Upload the first three files as assets of the same GitHub Release. The contents
of `release_notes.md` can be used as the Release description.
